---
title: "Populist Parties, who votes for them, and why"
author: "Declan Molloy"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dev = "png", dpi = 300, 
                      fig.width = 6, fig.asp = 0.618, fig.align = "center", out.width = "70%")
options(knitr.table.format = "html")
```

```{r packages, include=FALSE}
library(tidyverse)
library(haven)
library(ggrepel)
library(hrbrthemes)
library(modelr)
library(kableExtra)
```

#Identifying populist parties

There are two main datasets that attempt to classify parties around the world on various metrics, the Chapel Hill Expert Survey (CHES) and the Manifesto Project (previously known as the Comparative Manifesto Project). Neither explicitly code for populism, and so the challenge is to figure out a way to use the variables they do measure to try and come up with a systematic way to classify a party as populist or not. 

##Chapel Hill Expert Survey

To begin with, we'll look at the CHES dataset, which has asked country experts to rate various parties on different metrics. Inglehart and Norris have found that 13 variables from CHES neatly correspond to two separate cleavages: four can be reduced to an economic cleavage and nine can be reduced to a cultural cleavage. The variables summed to create the populism factor have been chosen to closely reflect ideological leanings associated with right wing populism. The results for every party is plotted below on both economic and populist scales, with parties classified as populist coloured in red, corresponding to higher cultural cleavage scores.

```{r parties, include=FALSE}
manifesto <- read_dta("data/MPDataset_MPDS2017a_stata14.dta")
parlgov.party <- read_csv("data/parlgov_party.csv")
ches.2014 <- read_dta("data/2014_CHES_dataset_means.dta") %>%
  mutate(party = party_name, year = 2014)
ches <- read_dta("data/1999-2014_CHES_dataset_means.dta") 
missing <- anti_join(ches.2014, ches, by = "party_id") %>% pull(party_id)
ches.combined <- bind_rows(ches, ches.2014 %>% filter(party_id %in% missing)) %>%
  rename(country.code = country) %>%
  mutate(country = case_when(country.code == 1 ~ "Belgium", 
                             country.code == 2 ~ "Denmark",
                             country.code == 3 ~ "Germany",
                             country.code == 4 ~ "Greece",
                             country.code == 5 ~ "Spain", 
                             country.code == 6 ~ "France",
                             country.code == 7 ~ "Ireland",
                             country.code == 8 ~ "Italy",
                             country.code == 10 ~ "Netherlands", 
                             country.code == 11 ~ "UK",
                             country.code == 12 ~ "Portugal",
                             country.code == 13 ~ "Austria",
                             country.code == 14 ~ "Finland", 
                             country.code == 16 ~ "Sweden",
                             country.code == 20 ~ "Bulgaria",
                             country.code == 21 ~ "Czech Republic",
                             country.code == 22 ~ "Estonia",
                             country.code == 23 ~ "Hungary",
                             country.code == 24 ~ "Latvia",
                             country.code == 25 ~ "Lithuania",
                             country.code == 26 ~ "Poland",
                             country.code == 27 ~ "Romania",
                             country.code == 28 ~ "Slovakia",
                             country.code == 29 ~ "Slovenia",
                             country.code == 31 ~ "Croatia",
                             country.code == 34 ~ "Turkey",
                             country.code == 35 ~ "Norway",
                             country.code == 36 ~ "Switzerland",
                             country.code == 37 ~ "Malta",
                             country.code == 38 ~ "Luxembourg",
                             country.code == 40 ~ "Cyprus")) 
party.link <- read_dta("data/link file for parties in EES.dta", encoding='latin1')
```
```{r party cross ref, include=FALSE}
# Manifesto ---------------------------------------------------------------
manifesto.unique <- manifesto %>%
  group_by(party) %>% 
  slice(which.max(edate)) %>%
  dplyr::ungroup() %>%
  mutate(cmp = party) %>%
  mutate(cmp = as.integer(cmp))

ches.unique <- ches.combined %>%
  select(country, eastwest, eumember, year, ches.id = party_id, cmp.id = cmp_id, party, vote, seat, electionyear, family, govt, 
         galtan, sociallifestyle, nationalism, civlib_laworder, multiculturalism, immigrate_policy, ethnic_minorities, religious_principle, urban_rural, 
         deregulation, econ_interven, redistribution, spendvtax) %>%
  #filter(year > 2005) %>%
  mutate(pop.mean = (rowMeans(select(., galtan, sociallifestyle, nationalism, 
                                     civlib_laworder, multiculturalism, immigrate_policy, 
                                     ethnic_minorities, religious_principle, urban_rural), na.rm = TRUE)) * 10,
         eco.mean = (rowMeans(select(., deregulation, econ_interven, redistribution, spendvtax), na.rm = TRUE)) * 10,
         pop.vote = if_else(pop.mean >= 75.35, 1, 0)) %>%
  group_by(ches.id) %>% 
  slice(which.max(year)) %>%
  dplyr::ungroup() %>%
  mutate(cmp.id = case_when(ches.id == 308 ~ 41521,
                            ches.id == 411 ~ 34020,
                            ches.id == 518 ~ 33096,
                            ches.id == 709 ~ 53021,
                            ches.id == 807 ~ 32221,
                            ches.id == 819 ~ 32421,
                            ches.id == 832 ~ 32329,
                            ches.id == 839 ~ 32320,
                            ches.id == 844 ~ 32630,
                            ches.id == 1107 ~ 51110,
                            ches.id == 2005 ~ 80062,
                            ches.id == 2012 ~ 80620,
                            ches.id == 2013 ~ 80061,
                            ches.id == 2014 ~ 80062,
                            ches.id == 2015 ~ 80630,
                            ches.id == 2016 ~ 80330,
                            ches.id == 2205 ~ 83952,
                            ches.id == 2410 ~ 87340,
                            ches.id == 2411 ~ 87620,
                            ches.id == 2412 ~ 87062,
                            ches.id == 2413 ~ 87630,
                            ches.id == 2414 ~ 87901,
                            ches.id == 2517 ~ 88630,
                            ches.id == 2611 ~ 92021,
                            ches.id == 2702 ~ 93031,
                            ches.id == 2709 ~ 93031, 
                            
                            TRUE ~ as.numeric(cmp.id))) %>%
  select(country, year, electionyear, party, ches = ches.id, cmp = cmp.id, vote, pop.mean, eco.mean, pop.vote) %>%
  mutate(ches = as.integer(ches), 
         cmp = as.integer(cmp))

parlgov.party.unique <- parlgov.party %>% 
  select(country_name, party_name_short, party_name_english, party_name, cmp, ches = chess, parlgov = party_id) %>%
  filter(!is.na(cmp)) %>% 
  arrange(ches) %>% 
  distinct(cmp, .keep_all = TRUE)

parlgov.unique.ches <- parlgov.party %>% 
  select(country_name, party_name_short, party_name_english, party_name, cmp, ches = chess, parlgov = party_id) %>%
  filter(!is.na(ches)) %>% 
  arrange(cmp) %>%
  distinct(ches, .keep_all = TRUE)

ches.parl <- left_join(ches.unique, parlgov.unique.ches, by = "ches") %>%
  mutate(cmp = if_else(is.na(cmp.x), cmp.y, cmp.x)) %>%
  select(-c(cmp.x, cmp.y))

ches.filter.na <- ches.parl %>% 
  filter(!(ches == 308 | ches == 411 | ches == 2005 | ches == 2709 | ches == 3113)) %>%
  filter(!is.na(cmp))

first.join <- left_join(manifesto.unique, ches.filter.na, by = "cmp")

doubled.up <- first.join %>% count(ches) %>% filter(n>1) %>% filter(!(is.na(ches))) %>% pull(ches)

second.join1 <- first.join %>%
  filter(!(ches %in% doubled.up))

temp.second.join <- first.join %>%
  filter(ches %in% doubled.up) %>%
  group_by(ches) %>%
  fill(parlgov) %>% fill(parlgov, .direction = "up") %>%
  ungroup()

third.join <- bind_rows(second.join1, temp.second.join)

party.link.unique <- party.link %>%
  select(country, prty_code, cmp = eu_manifesto, party_name) %>%
  filter(!is.na(cmp)) %>%
  distinct(cmp, .keep_all = TRUE) %>%
  mutate(cmp = as.integer(cmp))

manifesto.extended <- left_join(third.join, party.link.unique, by = "cmp") %>%
  mutate(state.market = (per401 + per402 + per407 + per414 + per505) - (per403 + per404 + per405 + per406 + per409 + per412 + per413 + per415 + per416 + per504), 
         prog.con = (per104 + per109 + per601 + per603 + per605 + per608) - (per105 + per106 + per107 + per501 + per503 + per602 + per604 + per607 + per705), 
         eco.lr = (per303 + per401 + per402 + per407 + per414 + per505 + per702 + per704) - (per404 + per406 + per413 + per415 + per503 + per504 + per701), 
         lib.auth = (per104 + per601 + per603 + per605 + per608) - (per105 + per602 + per604 + per607 + per705 + per416)) %>%
  select(country = countryname, party = partyname, partyabbrev, parfam, edate, edate.ches = electionyear, cmp, ches, parlgov,
         vote, pop.mean, pop.vote, prog.con, lib.auth, eco.mean, rile, state.market, eco.lr,planeco, markeco, welfare, per104, per601, per603, per605, per608, per105, per602, per604, per607, per705, per416) %>% 
  mutate(pop.cmp = 50 + (lib.auth/2)) %>%
  mutate(partyabbrev = if_else(cmp == 87630, "NSL", partyabbrev))

#corrplot(cor(manifesto.extended %>% select(-c(country, party, partyabbrev, edate, edate.ches, cmp, ches, parlgov, vote)), use = "complete.obs"), method = "circle")

# CHES --------------------------------------------------------------------

ches.extended <- ches.parl %>%
  left_join(manifesto.extended, by = "cmp") %>%
  select(country = country.x, year, electionyear, party_name_english, party_name, party.short = party.x, party.cmp = party.y, ches = ches.x, cmp, parlgov = parlgov.x, vote = vote.x, pop.mean = pop.mean.x, eco.mean = eco.mean.x, pop.vote = pop.vote.x, lib.auth, eco.lr) %>%
  filter(year > 2005)

rm(list=setdiff(ls(), c("manifesto.extended", "manifesto", "ches.combined", "ches.extended")))
``` 

```{r CHES-party-positions, fig.width=7, out.width = "100%", fig.asp = 1, cache = TRUE}
ggplot(data = ches.extended, aes(x = eco.mean, y = pop.mean, colour = factor(pop.vote))) + 
  geom_text_repel(aes(label = party.short), size = 1.8, box.padding = unit(0.1, 'lines'), point.padding = unit(.1, 'lines')) +
  geom_point(size = .005) + 
  coord_cartesian(ylim = c(0, 100), xlim = c(0, 100)) + 
  labs(x = "Left <<<< Economic Values Scale >>>> Right", 
       y = "Cosmopolitan Liberalism <<<< Cultural Values Scale >>>> Populism",
       colour = NULL, 
       caption = "Data from CHES 1999-2014") + 
  theme_ipsum() + theme(axis.title.x=element_text(hjust=.5), axis.title.y=element_text(hjust=.5)) + scale_color_brewer(labels =
                             c("Not Populist", "Populist"), palette = "Set1", direction=-1) +
  theme(legend.position = "top") + theme(plot.margin = unit(c(.35, .35, .35, .35), "cm"))
```

##Manifesto Project

A second large scale source of data on parties is the Manifesto Project which, as the name suggests, examines the electoral manifestos and other related materials of parties, coding based on how often certain topics are mentioned. Again, parties are plotted on an economic and populist scale. Parties have also been coloured according to whether they were previously classified as populist in the CHES dataset. As parties take a much smaller range of values and are thus more tightly clustered using the Manifesto project variables, it was not possible to label all of them. In order to highlight the differences in outcomes between the CHES and Manifesto Project results, political parties have been labelled that were classed as populist by the CHES data but scored lowly on the populist scale using the Manifesto Project data, as well as parties that scored highly but were not classified as populist by CHES. 

```{r cmp-parties, fig.width=7, out.width = "100%", cache = TRUE}
non.pop <- manifesto.extended %>% 
  filter(pop.vote == 0) %>%
  top_n(20, lib.auth) %>%
  pull(ches)

pop <- manifesto.extended %>% 
  filter(pop.vote == 1) %>%
  top_n(-10, lib.auth) %>% 
  pull(ches)

p <- ggplot(data = manifesto.extended %>% filter(!is.na(pop.vote)), aes(x = eco.lr, y = lib.auth, colour = factor(pop.vote)))
p + geom_point(size = .1) +
  geom_text_repel(data = subset(manifesto.extended, ches %in% non.pop | ches %in% pop), aes(label = partyabbrev), size = 2.8, box.padding = unit(0.1, 'lines'), point.padding = unit(.1, 'lines')) +
  labs(x = "Left <<<< Economic Values Scale >>>> Right", 
       y = "Cosmopolitan Liberalism <<<< Cultural Values Scale >>>> Populism",
       colour = "Classification from CHES") + 
  theme_ipsum() + theme(axis.title.x=element_text(hjust=.5), axis.title.y=element_text(hjust=.5)) + scale_color_brewer(labels =
                             c("Not Populist", "Populist"), palette = "Set1", direction=-1) +
  theme(legend.position = "top") + theme(plot.margin = unit(c(.35, .35, .35, .35), "cm"))
```

To further compare and contrast both datasets and methods, the Manifesto Project populist scores have been rescaled to a 0-100 scale, then each party plotted by their populist scores from the CHES data against the scores from the Manifesto data. Also included is a simple linear regression showing the relationship between the two scores, with some of the parties that have the highest absolute residuals from this linear regression labelled.

```{r compare, fig.width=7, out.width = "100%", cache = TRUE}
mod.compare <- lm(formula = pop.mean ~ pop.cmp, data = manifesto.extended)
grid <- manifesto.extended %>%
  data_grid(pop.cmp) %>%
  add_predictions(mod.compare)

manifesto.extended <- manifesto.extended %>%
  add_residuals(mod.compare)

p <- ggplot(manifesto.extended %>% filter(!is.na(pop.mean)), aes(x = pop.cmp, y = pop.mean))
p + geom_point(aes(colour = factor(pop.vote)), size = .1) + 
  geom_text_repel(data = subset(manifesto.extended, resid > 28 | resid < -25), aes(label = partyabbrev, colour = factor(pop.vote)), size = 3.5, box.padding = unit(0.1, 'lines'), point.padding = unit(.1, 'lines')) +
  geom_smooth(method = "lm") + 
  labs(x = "Manifesto Project - Populism score", 
       y = "CHES - Populism score",
       colour = "Classification from CHES") + 
  theme_ipsum() + theme(axis.title.x=element_text(hjust=.5), axis.title.y=element_text(hjust=.5)) + scale_color_brewer(labels =
                             c("Not Populist", "Populist"), palette = "Set1", direction=-1) +
  coord_cartesian(ylim = c(0, 100), xlim = c(35, 77.5)) + 
  theme(legend.position = "top") + theme(plot.margin = unit(c(.35, .35, .35, .35), "cm"))
```

Finally, I've plotted the residuals themselves, with the same parties labelled. Parties above 0 means a party's CHES populism score is higher (more populist) than expected given its score from the Manifesto Project.

```{r resid-compare, fig.width=7, out.width = "100%", cache = TRUE}
ggplot(manifesto.extended %>% filter(!is.na(pop.vote)), aes(pop.cmp, resid, colour = factor(pop.vote))) + 
  geom_ref_line(h = 0, colour = "gray70") +
  geom_point(size = .1) +
  geom_text_repel(data = subset(manifesto.extended, resid > 28 | resid < -25), aes(label = partyabbrev), size = 3.5, box.padding = unit(0.1, 'lines'), point.padding = unit(.1, 'lines')) + 
  labs(x = "Manifesto Project - Populism score", 
       y = "Residual error",
       colour = "Classification from CHES") + 
  theme_ipsum() + theme(axis.title.x=element_text(hjust=.5), axis.title.y=element_text(hjust=.5)) + scale_color_brewer(labels =
                             c("Not Populist", "Populist"), palette = "Set1", direction=-1) +
  theme(legend.position = "top") + theme(plot.margin = unit(c(.35, .35, .35, .35), "cm"))
```

##Which to use?

Looking at these comparisons, it becomes clear that the Manifesto Project populism score is worse at identifying populist radical right parties than the CHES score. The plot of its party classifications shows several widely accepted populist parties, including *Ataka* in Bulgaria, *AfD* in Germany and *Lega Nord* in Italy, with populist scores close to the mean of all parties. This difference is even more stark in when we look at the residuals, where we can see that the parties rated higher by CHES include other populist parties, such as *Jobbik* in Hungary and the *People's Party – Dan Diaconescu* in Romania. Parties that are rated as higher by the Manifesto Project metric include more left-leaning parties, such as the *Left Bloc* in Portugal and the *Green Party* in Sweden. Given this project is focused on radical right populist parties, I use the CHES data to classify populist parties. See the appendix for a full table of populist parties. 

#Who votes for them? 

Now that we have identified which parties fall under the banner of populist radical right parties, it is time to turn our eye to who is voting for them. In particular, we want to know if certain political generations or age groups are more likely to vote for populist radical right parties than other age groups. This leads to my main finding: **contrary to popular belief, young voters are actually more likely to vote for populist parties.** Given this counter-intuitive result, the underlying data is investigated in order to prove that this result was not driven by statistical outliers. The conclusion still stands in the face of this analysis; younger voters are indeed more likely to vote for populist parties. 

To figure out which age groups and generations are voting for the populist parties identified in the last chapter, we need data about which party people have voted for, and how old they were when they did so. The European Social Survey is a survey that asks a variety of questions about attitudes and voting behaviour to respondents across Europe. It has been run biennially since 2002 with the most recent release of data from 2014, meaning there are 7 waves of data with 331,871 individual respondents. Such a large sample means that we can accurately trace the age profiles of populist party voters even though many of these parties receive quite small vote shares. Respondents were weighted using both post-stratification weighting, which attempts to correct for non-response bias by weighting respondents so that the overall sample matches the composition of the general public in demographics such as age-group, gender, education, and regional distribution, as well as by country weights, which adjusts for the fact that different countries in Europe have different populations, but the sample size in each country is approximately the same. From here, the voting data was recoded such that it matched the CHES dataset. Countries that were not in the CHES dataset as well as non-voters were discarded, leaving us with 171,341 respondents who both voted and lived in a country covered by CHES. Respondents were then grouped by age and year of birth, with the weighted percentage of people who voted for a populist party calculated for each age and birth year. Finally, a simple locally weighted regression (LOESS) curve was plotted to fit this data for each wave of the ESS, resulting in the finding that young people are more likely to vote for populist parties than older people, graphed below. 

```{r load ess, cache=TRUE, include=FALSE}
ess <- read_dta(unz("data/ESS1-7e01.zip", "ESS1-7e01.dta"), encoding='latin1') %>%
  mutate(source = "ESS") %>%
  mutate(ches = case_when(prtvtat == 1 ~ 1301, prtvtat == 2 ~ 1302, prtvtat == 3 ~ 1303, prtvtat == 4 ~ 1304, prtvtat == 5 ~ 1306, prtvtat == 6 ~ 1399,
                          prtvtaat == 1 ~ 1301, prtvtaat == 2 ~ 1302, prtvtaat == 3 ~ 1303, prtvtaat == 4 ~ 1307, prtvtaat == 5 ~ 1304, prtvtaat == 6 ~ 1306, prtvtaat == 7 ~ 1399, prtvtaat == 8 ~ 1399,
                          prtvtbat == 1 ~ 1301, prtvtbat == 2 ~ 1302, prtvtbat == 3 ~ 1303, prtvtbat == 4 ~ 1307, prtvtbat == 5 ~ 1304, prtvtbat == 6 ~ 1399, prtvtbat == 7 ~ 1306, prtvtbat == 8 ~ 1399, prtvtbat == 9 ~ 1310, prtvtbat == 10 ~ 1399,
                          prtvtbe == 1 ~ 105, prtvtbe == 2 ~ 109, prtvtbe == 3 ~ 103, prtvtbe == 4 ~ 199, prtvtbe == 5 ~ 107, prtvtbe == 6 ~ 110, prtvtbe == 7 ~ 119, prtvtbe == 8 ~ 112, prtvtbe == 9 ~ 199, prtvtbe == 11 ~ 104, prtvtbe == 12 ~ 108, prtvtbe == 13 ~ 106, prtvtbe == 14 ~ 102, prtvtbe == 15 ~ 115, prtvtbe == 16 ~ 119, prtvtbe == 17 ~ 199,
                          prtvtabe == 1 ~ 105, prtvtabe == 2 ~ 109, prtvtabe == 3 ~ 110, prtvtabe == 4 ~ 199, prtvtabe == 5 ~ 103, prtvtabe == 6 ~ 199, prtvtabe == 7 ~ 112, prtvtabe == 8 ~ 107, prtvtabe == 9 ~ 108, prtvtabe == 10 ~ 104, prtvtabe == 11 ~ 115, prtvtabe == 12 ~ 106, prtvtabe == 13 ~ 102, prtvtabe == 14 ~ 199,
                          prtvtbbe == 1 ~ 105, prtvtbbe == 2 ~ 109, prtvtbbe == 4 ~ 117, prtvtbbe == 5 ~ 103, prtvtbbe == 7 ~ 112, prtvtbbe == 8 ~ 107, prtvtbbe == 9 ~ 108, prtvtbbe == 10 ~ 104, prtvtbbe == 11 ~ 115, prtvtbbe == 12 ~ 106, prtvtbbe == 13 ~ 102, prtvtbbe == 14 ~ 199,
                          prtvtcbe == 1 ~ 105, prtvtcbe == 2 ~ 109, prtvtcbe == 3 ~ 110, prtvtcbe == 4 ~ 117, prtvtcbe == 5 ~ 103, prtvtcbe == 6 ~ 199, prtvtcbe == 7 ~ 112, prtvtcbe == 8 ~ 107, prtvtcbe == 9 ~ 108, prtvtcbe == 10 ~ 104, prtvtcbe == 11 ~ 115, prtvtcbe == 12 ~ 106, prtvtcbe == 13 ~ 102, prtvtcbe == 14 ~ 199, prtvtcbe == 15 ~ 120, prtvtcbe == 16 ~ 199, prtvtcbe == 17 ~ 199, prtvtcbe == 18 ~ 199,
                          prtvtbg == 1 ~ 2003, prtvtbg == 2 ~ 2004, prtvtbg == 3 ~ 2099, prtvtbg == 4 ~ 2008, prtvtbg == 5 ~ 2001, prtvtbg == 6 ~ 2002, prtvtbg == 7 ~ 2009, prtvtbg == 8 ~ 2099, prtvtbg == 9 ~ 2099, prtvtbg == 10 ~ 2007, prtvtbg == 11 ~ 2099,
                          prtvtabg == 1 ~ 2003, prtvtabg == 2 ~ 2004, prtvtabg == 3 ~ 2099, prtvtabg == 4 ~ 2008, prtvtabg == 5 ~ 2001, prtvtabg == 6 ~ 2002, prtvtabg == 7 ~ 2009, prtvtabg == 8 ~ 2099, prtvtabg == 9 ~ 2099, prtvtabg == 10 ~ 2007, prtvtabg == 11 ~ 2099,
                          prtvtbbg == 1 ~ 2010, prtvtbbg == 2 ~ 2003, prtvtbbg == 3 ~ 2004, prtvtbbg == 4 ~ 2002, prtvtbbg == 5 ~ 2007, prtvtbbg == 6 ~ 2012, prtvtbbg == 7 ~ 2001, prtvtbbg == 8 ~ 2011, prtvtbbg == 9 ~ 2099, prtvtbbg == 10 ~ 2099, prtvtbbg == 11 ~ 2099, prtvtbbg == 12 ~ 2099, prtvtbbg == 13 ~ 2099, prtvtbbg == 14 ~ 2099, prtvtbbg == 15 ~ 2099, prtvtbbg == 16 ~ 2099, prtvtbbg == 17 ~ 2099,
                          prtvtcbg == 1 ~ 2010, prtvtcbg == 2 ~ 2003, prtvtcbg == 3 ~ 2007, prtvtcbg == 4 ~ 2012, prtvtcbg == 5 ~ 2005, prtvtcbg == 6 ~ 2099, prtvtcbg == 7 ~ 2014, prtvtcbg == 8 ~ 2099, prtvtcbg == 9 ~ 2099, prtvtbbg == 10 ~ 2099, prtvtbbg == 11 ~ 2099, prtvtbbg == 12 ~ 2099, prtvtbbg == 13 ~ 2099,
                          prtvtch == 1 ~ 3603, prtvtch == 2 ~ 3604, prtvtch == 3 ~ 3602, prtvtch == 4 ~ 3601, prtvtch == 5 ~ 3603, prtvtch == 6 ~ 3699, prtvtch == 7 ~ 3607, prtvtch == 8 ~ 3611, prtvtch == 9 ~ 3699, prtvtch == 10 ~ 3605, prtvtch == 11 ~ 3699, prtvtch == 12 ~ 3608, prtvtch == 13 ~ 3699, prtvtch == 14 ~ 3699, prtvtch == 15 ~ 3611, prtvtch == 16 ~ 3699,
                          prtvtach == 1 ~ 3603, prtvtach == 2 ~ 3604, prtvtach == 3 ~ 3602, prtvtach == 4 ~ 3601, prtvtach == 5 ~ 3603, prtvtach == 7 ~ 3607, prtvtach == 8 ~ 3611, prtvtach == 9 ~ 3699, prtvtach == 10 ~ 3605, prtvtach == 11 ~ 3699, prtvtach == 12 ~ 3608, prtvtach == 13 ~ 3699, prtvtach == 14 ~ 3699, prtvtach == 15 ~ 3611, prtvtach == 16 ~ 3699,
                          prtvtbch == 1 ~ 3603, prtvtbch == 2 ~ 3604, prtvtbch == 3 ~ 3602, prtvtbch == 4 ~ 3601, prtvtbch == 5 ~ 3603, prtvtbch == 6 ~ 3611, prtvtbch == 7 ~ 3699, prtvtbch == 8 ~ 3605, prtvtbch == 9 ~ 3606, prtvtbch == 10 ~ 3699, prtvtbch == 11 ~ 3608, prtvtbch == 12 ~ 3607, prtvtbch == 13 ~ 3610, prtvtbch == 14 ~ 3699, prtvtbch == 16 ~ 3699,
                          prtvtcch == 1 ~ 3603, prtvtcch == 2 ~ 3604, prtvtcch == 3 ~ 3602, prtvtcch == 4 ~ 3601, prtvtcch == 5 ~ 3603, prtvtcch == 6 ~ 3611, prtvtcch == 7 ~ 3699, prtvtcch == 8 ~ 3605, prtvtcch == 9 ~ 3606, prtvtcch == 10 ~ 3699, prtvtcch == 11 ~ 3608, prtvtcch == 12 ~ 3607, prtvtcch == 13 ~ 3610, prtvtcch == 14 ~ 3699, prtvtcch == 19 ~ 3699, prtvtcch == 20 ~ 3699,
                          prtvtdch == 1 ~ 3601, prtvtdch == 2 ~ 3602, prtvtdch == 3 ~ 3603, prtvtdch == 4 ~ 3604, prtvtdch == 5 ~ 3605, prtvtdch == 6 ~ 3606, prtvtdch == 7 ~ 3612, prtvtdch == 8 ~ 3607, prtvtdch == 9 ~ 3608, prtvtdch == 10 ~ 3610, prtvtdch == 11 ~ 3699, prtvtdch == 12 ~ 3699, prtvtdch == 13 ~ 3611, prtvtdch == 14 ~ 3699, prtvtdch == 15 ~ 3699, prtvtdch == 16 ~ 3699, prtvtdch == 17 ~ 3699, prtvtdch == 20 ~ 3699,
                          prtvtech == 1 ~ 3601, prtvtech == 2 ~ 3602, prtvtech == 3 ~ 3603, prtvtech == 4 ~ 3604, prtvtech == 5 ~ 3605, prtvtech == 6 ~ 3606, prtvtech == 7 ~ 3612, prtvtech == 8 ~ 3607, prtvtech == 9 ~ 3608, prtvtech == 10 ~ 3610, prtvtech == 11 ~ 3699, prtvtech == 12 ~ 3699, prtvtech == 13 ~ 3611, prtvtech == 14 ~ 3699, prtvtech == 15 ~ 3699, prtvtech == 16 ~ 3699, prtvtech == 17 ~ 3699, prtvtech == 18 ~ 3699, prtvtech == 20 ~ 3699,
                          prtvtcy == 1 ~ 4003, prtvtcy == 2 ~ 4004, prtvtcy == 3 ~ 4001, prtvtcy == 4 ~ 4002, prtvtcy == 5 ~ 4006, prtvtcy == 6 ~ 4099, prtvtcy == 7 ~ 4005, prtvtcy == 8 ~ 4099,
                          prtvtacy == 1 ~ 4003, prtvtacy == 2 ~ 4004, prtvtacy == 3 ~ 4001, prtvtacy == 4 ~ 4002, prtvtacy == 5 ~ 4006, prtvtacy == 6 ~ 4005, prtvtacy == 7 ~ 4099,
                          prtvtcz == 1 ~ 2101, prtvtcz == 2 ~ 2102, prtvtcz == 3 ~ 2199, prtvtcz == 4 ~ 2199, prtvtcz == 5 ~ 2199, prtvtcz == 6 ~ 2199, prtvtcz == 7 ~ 2106, prtvtcz == 8 ~ 2102, prtvtcz == 9 ~ 2103, prtvtcz == 10 ~ 2104, prtvtcz == 11 ~ 2199, prtvtcz == 12 ~ 2199, prtvtcz == 13 ~ 2107, prtvtcz == 14 ~ 2199,
                          prtvtacz == 1 ~ 2103, prtvtacz == 2 ~ 2101, prtvtacz == 3 ~ 2107, prtvtacz == 4 ~ 2104, prtvtacz == 5 ~ 2102, prtvtacz == 6 ~ 2199,
                          prtvtbcz == 1 ~ 2103, prtvtbcz == 2 ~ 2101, prtvtbcz == 3 ~ 2107, prtvtbcz == 4 ~ 2104, prtvtbcz == 5 ~ 2109, prtvtbcz == 6 ~ 2110, prtvtbcz == 7 ~ 2102, prtvtbcz == 8 ~ 2199,
                          prtvtccz == 1 ~ 2103, prtvtccz == 2 ~ 2101, prtvtccz == 3 ~ 2109, prtvtccz == 4 ~ 2110, prtvtccz == 5 ~ 2102, prtvtccz == 8 ~ 2199,
                          prtvtdcz == 1 ~ 2103, prtvtdcz == 2 ~ 2101, prtvtdcz == 3 ~ 2109, prtvtdcz == 4 ~ 2111, prtvtdcz == 5 ~ 2102, prtvtdcz == 6 ~ 2104, prtvtdcz == 7 ~ 2112, prtvtdcz == 8 ~ 2199,
                          prtvde1 == 1 ~ 302, prtvde1 == 2 ~ 301, prtvde1 == 3 ~ 304, prtvde1 == 4 ~ 303, prtvde1 == 5 ~ 306, prtvde1 == 6 ~ 305, prtvde1 == 7 ~ 399,
                          prtvade1 == 1 ~ 302, prtvade1 == 2 ~ 301, prtvade1 == 3 ~ 304, prtvade1 == 4 ~ 303, prtvade1 == 5 ~ 306, prtvade1 == 6 ~ 305, prtvade1 == 7 ~ 309, prtvade1 == 8 ~ 399,
                          prtvbde1 == 1 ~ 302, prtvbde1 == 2 ~ 301, prtvbde1 == 3 ~ 304, prtvbde1 == 4 ~ 303, prtvbde1 == 5 ~ 306, prtvbde1 == 6 ~ 305, prtvbde1 == 7 ~ 309, prtvbde1 == 8 ~ 399,
                          prtvcde1 == 1 ~ 302, prtvcde1 == 2 ~ 301, prtvcde1 == 3 ~ 304, prtvcde1 == 4 ~ 303, prtvcde1 == 5 ~ 306, prtvcde1 == 6 ~ 305, prtvcde1 == 7 ~ 309, prtvcde1 == 8 ~ 399,
                          prtvdde1 == 1 ~ 302, prtvdde1 == 2 ~ 301, prtvdde1 == 3 ~ 304, prtvdde1 == 4 ~ 303, prtvdde1 == 5 ~ 306, prtvdde1 == 6 ~ 305, prtvdde1 == 7 ~ 309, prtvdde1 == 8 ~ 311, prtvdde1 == 9 ~ 399,
                          prtvede1 == 1 ~ 301, prtvede1 == 2 ~ 302, prtvede1 == 3 ~ 306, prtvede1 == 4 ~ 304, prtvede1 == 5 ~ 303, prtvede1 == 6 ~ 310, prtvede1 == 7 ~ 311, prtvede1 == 8 ~ 309, prtvede1 == 9 ~ 399,
                          prtvde2 == 1 ~ 302, prtvde2 == 2 ~ 301, prtvde2 == 3 ~ 304, prtvde2 == 4 ~ 303, prtvde2 == 5 ~ 306, prtvde2 == 6 ~ 305, prtvde2 == 7 ~ 399,
                          prtvade2 == 1 ~ 302, prtvade2 == 2 ~ 301, prtvade2 == 3 ~ 304, prtvade2 == 4 ~ 303, prtvade2 == 5 ~ 306, prtvade2 == 6 ~ 305, prtvade2 == 7 ~ 309, prtvade2 == 8 ~ 399,
                          prtvbde2 == 1 ~ 302, prtvbde2 == 2 ~ 301, prtvbde2 == 3 ~ 304, prtvbde2 == 4 ~ 303, prtvbde2 == 5 ~ 306, prtvbde2 == 6 ~ 305, prtvbde2 == 7 ~ 309, prtvbde2 == 8 ~ 399,
                          prtvcde2 == 1 ~ 302, prtvcde2 == 2 ~ 301, prtvcde2 == 3 ~ 304, prtvcde2 == 4 ~ 303, prtvcde2 == 5 ~ 306, prtvcde2 == 6 ~ 305, prtvcde2 == 7 ~ 309, prtvcde2 == 8 ~ 399,
                          prtvdde2 == 1 ~ 302, prtvdde2 == 2 ~ 301, prtvdde2 == 3 ~ 304, prtvdde2 == 4 ~ 303, prtvdde2 == 5 ~ 306, prtvdde2 == 6 ~ 305, prtvdde2 == 7 ~ 309, prtvdde2 == 8 ~ 311, prtvdde2 == 9 ~ 399,
                          prtvede2 == 1 ~ 301, prtvede2 == 2 ~ 302, prtvede2 == 3 ~ 306, prtvede2 == 4 ~ 304, prtvede2 == 5 ~ 303, prtvede2 == 6 ~ 310, prtvede2 == 7 ~ 311, prtvede2 == 8 ~ 309, prtvede2 == 9 ~ 399,
                          prtvtdk == 1 ~ 201, prtvtdk == 2 ~ 202, prtvtdk == 3 ~ 203, prtvtdk == 4 ~ 204, prtvtdk == 5 ~ 206, prtvtdk == 6 ~ 215, prtvtdk == 7 ~ 210, prtvtdk == 8 ~ 211, prtvtdk == 9 ~ 212, prtvtdk == 10 ~ 213, prtvtdk == 11 ~ 299,
                          prtvtadk == 1 ~ 201, prtvtadk == 2 ~ 202, prtvtadk == 3 ~ 203, prtvtadk == 4 ~ 204, prtvtadk == 5 ~ 206, prtvtadk == 6 ~ 215, prtvtadk == 7 ~ 210, prtvtadk == 8 ~ 211, prtvtadk == 9 ~ 212, prtvtadk == 10 ~ 213, prtvtadk == 11 ~ 299,
                          prtvtbdk == 1 ~ 201, prtvtbdk == 2 ~ 202, prtvtbdk == 3 ~ 203, prtvtbdk == 4 ~ 206, prtvtbdk == 5 ~ 215, prtvtbdk == 6 ~ 210, prtvtbdk == 7 ~ 211, prtvtbdk == 8 ~ 218, prtvtbdk == 9 ~ 213, prtvtbdk == 10 ~ 299,
                          prtvtcdk == 1 ~ 201, prtvtcdk == 2 ~ 202, prtvtcdk == 3 ~ 203, prtvtcdk == 4 ~ 206, prtvtcdk == 5 ~ 215, prtvtcdk == 6 ~ 210, prtvtcdk == 7 ~ 211, prtvtcdk == 8 ~ 218, prtvtcdk == 9 ~ 213, prtvtcdk == 10 ~ 299,
                          prtvtee == 1 ~ 2201, prtvtee == 2 ~ 2202, prtvtee == 3 ~ 2203, prtvtee == 4 ~ 2201, prtvtee == 5 ~ 2204, prtvtee == 6 ~ 2206, prtvtee == 7 ~ 2299, prtvtee == 8 ~ 2299, prtvtee == 9 ~ 2299, prtvtee == 10 ~ 2299, prtvtee == 11 ~ 2299, prtvtee == 12 ~ 2299, prtvtee == 13 ~ 2299,
                          prtvtaee == 1 ~ 2201, prtvtaee == 2 ~ 2202, prtvtaee == 3 ~ 2203, prtvtaee == 4 ~ 2201, prtvtaee == 5 ~ 2204, prtvtaee == 6 ~ 2206, prtvtaee == 7 ~ 2205, 
                          prtvtbee == 1 ~ 2201, prtvtbee == 2 ~ 2202, prtvtbee == 3 ~ 2203, prtvtbee == 4 ~ 2206, prtvtbee == 5 ~ 2204, prtvtbee == 6 ~ 2207, prtvtbee == 7 ~ 2299, prtvtbee == 8 ~ 2205, prtvtbee == 9 ~ 2299, prtvtbee == 10 ~ 2299,
                          prtvtcee == 1 ~ 2201, prtvtcee == 2 ~ 2202, prtvtcee == 3 ~ 2203, prtvtcee == 4 ~ 2206, prtvtcee == 5 ~ 2204, prtvtcee == 6 ~ 2207, prtvtcee == 7 ~ 2299, prtvtcee == 8 ~ 2298, prtvtcee == 9 ~ 2298, prtvtcee == 10 ~ 2299, prtvtcee == 11 ~ 2299, 
                          prtvtdee == 1 ~ 2201, prtvtdee == 2 ~ 2202, prtvtdee == 3 ~ 2203, prtvtdee == 4 ~ 2206, prtvtdee == 5 ~ 2204, prtvtdee == 6 ~ 2207, prtvtdee == 7 ~ 2299, prtvtdee == 8 ~ 2298, prtvtdee == 9 ~ 2205, prtvtdee == 10 ~ 2299, prtvtdee == 11 ~ 2299, 
                          prtvteee == 1 ~ 2203, prtvteee == 2 ~ 2202, prtvteee == 3 ~ 2201, prtvteee == 4 ~ 2204, prtvteee == 5 ~ 2207, prtvteee == 6 ~ 2206, prtvteee == 7 ~ 2299, prtvteee == 8 ~ 2299, prtvteee == 9 ~ 2298, prtvteee == 10 ~ 2299,
                          prtvtes == 1 ~ 502, prtvtes == 2 ~ 501, prtvtes == 3 ~ 504, prtvtes == 4 ~ 505, prtvtes == 5 ~ 511, prtvtes == 6 ~ 518, prtvtes == 7 ~ 506, prtvtes == 8 ~ 507, prtvtes == 9 ~ 513, prtvtes == 10 ~ 517, prtvtes == 11 ~ 516, prtvtes == 12 ~ 520, prtvtes == 68 ~ 599,
                          prtvtaes == 1 ~ 502, prtvtaes == 2 ~ 501, prtvtaes == 3 ~ 504, prtvtaes == 4 ~ 505, prtvtaes == 5 ~ 511, prtvtaes == 6 ~ 518, prtvtaes == 7 ~ 506, prtvtaes == 8 ~ 507, prtvtaes == 9 ~ 513, prtvtaes == 10 ~ 517, prtvtaes == 11 ~ 516, prtvtaes == 12 ~ 520, prtvtaes == 13 ~ 506, prtvtaes == 74 ~ 599,
                          prtvtbes == 1 ~ 502, prtvtbes == 2 ~ 501, prtvtbes == 3 ~ 504, prtvtbes == 4 ~ 505, prtvtbes == 5 ~ 511, prtvtbes == 6 ~ 506, prtvtbes == 7 ~ 513, prtvtbes == 8 ~ 517, prtvtbes == 9 ~ 506, prtvtbes == 10 ~ 523, prtvtbes == 74 ~ 599, 
                          prtvtces == 1 ~ 502, prtvtces == 2 ~ 501, prtvtces == 3 ~ 505, prtvtces == 4 ~ 504, prtvtces == 5 ~ 524, prtvtces == 6 ~ 523, prtvtces == 7 ~ 506, prtvtces == 8 ~ 511, prtvtces == 9 ~ 513, prtvtces == 10 ~ 517, prtvtces == 11 ~ 599, prtvtces == 12 ~ 526, prtvtces == 13 ~ 506, prtvtces == 14 ~ 599,
                          prtvtfi == 1 ~ 1402, prtvtfi == 2 ~ 1406, prtvtfi == 3 ~ 1499, prtvtfi == 4 ~ 1403, prtvtfi == 5 ~ 1405, prtvtfi == 6 ~ 1409, prtvtfi == 7 ~ 1499, prtvtfi == 8 ~ 1408, prtvtfi == 9 ~ 1401, prtvtfi == 10 ~ 1404, prtvtfi == 11 ~ 1499, prtvtfi == 12 ~ 1499, prtvtfi == 13 ~ 1499, prtvtfi == 14 ~ 1499,
                          prtvtafi == 1 ~ 1402, prtvtafi == 2 ~ 1406, prtvtafi == 3 ~ 1499, prtvtafi == 4 ~ 1403, prtvtafi == 5 ~ 1405, prtvtafi == 6 ~ 1409, prtvtafi == 7 ~ 1408, prtvtafi == 8 ~ 1401, prtvtafi == 9 ~ 1404, prtvtafi == 10 ~ 1499, prtvtafi == 11 ~ 1499, prtvtafi == 12 ~ 1499,
                          prtvtbfi == 1 ~ 1402, prtvtbfi == 2 ~ 1406, prtvtbfi == 3 ~ 1499, prtvtbfi == 4 ~ 1403, prtvtbfi == 5 ~ 1405, prtvtbfi == 6 ~ 1409, prtvtbfi == 7 ~ 1499, prtvtbfi == 8 ~ 1499, prtvtbfi == 9 ~ 1411, prtvtbfi == 10 ~ 1499, prtvtbfi == 11 ~ 1499, prtvtbfi == 12 ~ 1499, prtvtbfi == 13 ~ 1408, prtvtbfi == 14 ~ 1401, prtvtbfi == 15 ~ 1404, prtvtbfi == 16 ~ 1499, prtvtbfi == 17 ~ 1499, prtvtbfi == 18 ~ 1499, prtvtbfi == 19 ~ 1499,
                          prtvtcfi == 1 ~ 1402, prtvtcfi == 2 ~ 1406, prtvtcfi == 3 ~ 1403, prtvtcfi == 4 ~ 1405, prtvtcfi == 5 ~ 1409, prtvtcfi == 6 ~ 1499, prtvtcfi == 7 ~ 1499, prtvtcfi == 8 ~ 1499, prtvtcfi == 9 ~ 1411, prtvtcfi == 10 ~ 1499, prtvtcfi == 11 ~ 1499, prtvtcfi == 12 ~ 1408, prtvtcfi == 13 ~ 1401, prtvtcfi == 14 ~ 1404, prtvtcfi == 15 ~ 1499, prtvtcfi == 16 ~ 1499, prtvtcfi == 17 ~ 1499, prtvtcfi == 18 ~ 1499,
                          prtvtfr == 1 ~ 619, prtvtfr == 2 ~ 615, prtvtfr == 3 ~ 610, prtvtfr == 4 ~ 614, prtvtfr == 5 ~ 614, prtvtfr == 6 ~ 699, prtvtfr == 7 ~ 620, prtvtfr == 8 ~ 612, prtvtfr == 9 ~ 601, prtvtfr == 10 ~ 602, prtvtfr == 11 ~ 612, prtvtfr == 12 ~ 609, prtvtfr == 13 ~ 613, prtvtfr == 14 ~ 605, prtvtfr == 15 ~ 699, prtvtfr == 16 ~ 699,
                          prtvtafr == 1 ~ 619, prtvtafr == 2 ~ 615, prtvtafr == 3 ~ 610, prtvtafr == 4 ~ 614, prtvtafr == 5 ~ 614, prtvtafr == 6 ~ 699, prtvtafr == 7 ~ 620, prtvtafr == 8 ~ 612, prtvtafr == 9 ~ 601, prtvtafr == 10 ~ 602, prtvtafr == 11 ~ 612, prtvtafr == 12 ~ 609, prtvtafr == 13 ~ 613, prtvtafr == 14 ~ 605, prtvtafr == 15 ~ 699, prtvtafr == 16 ~ 699,
                          prtvtbfr == 1 ~ 619, prtvtbfr == 2 ~ 610, prtvtbfr == 3 ~ 614, prtvtbfr == 4 ~ 614, prtvtbfr == 5 ~ 612, prtvtbfr == 6 ~ 621, prtvtbfr == 7 ~ 601, prtvtbfr == 8 ~ 602, prtvtbfr == 9 ~ 603, prtvtbfr == 10 ~ 613, prtvtbfr == 11 ~ 609, prtvtbfr == 12 ~ 605, prtvtbfr == 13 ~ 699, prtvtbfr == 14 ~ 699, prtvtbfr == 15 ~ 699, prtvtbfr == 16 ~ 699,
                          prtvtcfr == 1 ~ 621, prtvtcfr == 2 ~ 610, prtvtcfr == 3 ~ 622, prtvtcfr == 4 ~ 699, prtvtcfr == 5 ~ 614, prtvtcfr == 6 ~ 603, prtvtcfr == 7 ~ 601, prtvtcfr == 8 ~ 612, prtvtcfr == 9 ~ 601, prtvtcfr == 10 ~ 609, prtvtcfr == 11 ~ 613, prtvtcfr == 12 ~ 605, prtvtcfr == 13 ~ 699, prtvtcfr == 14 ~ 699,
                          prtvtgb == 1 ~ 1101, prtvtgb == 2 ~ 1102, prtvtgb == 3 ~ 1104, prtvtgb == 4 ~ 1105, prtvtgb == 5 ~ 1106, prtvtgb == 6 ~ 1107, prtvtgb == 7 ~ 1199, prtvtgb == 11 ~ 1199, prtvtgb == 12 ~ 1199, prtvtgb == 13 ~ 707, prtvtgb == 14 ~ 1199, prtvtgb == 15 ~ 1199, prtvtgb == 16 ~ 1199, prtvtgb == 17 ~ 1199, prtvtgb == 18 ~ 1199, prtvtgb == 19 ~ 1199, prtvtgb == 20 ~ 1199, prtvtgb == 21 ~ 1199, prtvtgb == 22 ~ 1199,
                          prtvtagb == 1 ~ 1101, prtvtagb == 2 ~ 1102, prtvtagb == 3 ~ 1104, prtvtagb == 4 ~ 1105, prtvtagb == 5 ~ 1106, prtvtagb == 6 ~ 1107, prtvtagb == 7 ~ 1109, prtvtagb == 8 ~ 1108, prtvtagb == 9 ~ 1199, prtvtagb == 11 ~ 1199, prtvtagb == 12 ~ 1199, prtvtagb == 13 ~ 707, prtvtagb == 14 ~ 1199, prtvtagb == 15 ~ 1199, prtvtagb == 16 ~ 1199, prtvtagb == 17 ~ 1199, prtvtagb == 18 ~ 1199, prtvtagb == 19 ~ 1199, prtvtagb == 20 ~ 1199, prtvtagb == 21 ~ 1199, prtvtagb == 22 ~ 1199,
                          prtvtbgb == 1 ~ 1101, prtvtbgb == 2 ~ 1102, prtvtbgb == 3 ~ 1104, prtvtbgb == 4 ~ 1105, prtvtbgb == 5 ~ 1106, prtvtbgb == 6 ~ 1107, prtvtbgb == 7 ~ 1108, prtvtbgb == 8 ~ 1199, prtvtbgb == 9 ~ 1199, prtvtbgb == 10 ~ 1199, prtvtbgb == 11 ~ 707, prtvtbgb == 12 ~ 1199, prtvtbgb == 13 ~ 1199, prtvtbgb == 14 ~ 1199, prtvtbgb == 15 ~ 1199, prtvtbgb == 16 ~ 1199, prtvtbgb == 17 ~ 1199, prtvtbgb == 18 ~ 1199,
                          prtvtgr == 1 ~ 401, prtvtgr == 2 ~ 402, prtvtgr == 3 ~ 404, prtvtgr == 4 ~ 403, prtvtgr == 5 ~ 409, prtvtgr == 6 ~ 499,
                          prtvtagr == 1 ~ 401, prtvtagr == 2 ~ 402, prtvtagr == 3 ~ 404, prtvtagr == 4 ~ 403, prtvtagr == 5 ~ 409, prtvtagr == 6 ~ 410, prtvtagr == 7 ~ 499,
                          prtvtbgr == 1 ~ 401, prtvtbgr == 2 ~ 402, prtvtbgr == 3 ~ 404, prtvtbgr == 4 ~ 403, prtvtbgr == 5 ~ 410, prtvtbgr == 6 ~ 411, prtvtbgr == 7 ~ 499,
                          prtvtcgr == 1 ~ 401, prtvtcgr == 2 ~ 402, prtvtcgr == 3 ~ 404, prtvtcgr == 4 ~ 410, prtvtcgr == 5 ~ 403, prtvtcgr == 6 ~ 411, prtvtcgr == 7 ~ 499,
                          prtvthr == 1 ~ 3101, prtvthr == 2 ~ 3102, prtvthr == 3 ~ 3105, prtvthr == 4 ~ 3103, prtvthr == 5 ~ 3104, prtvthr == 6 ~ 3106, prtvthr == 7 ~ 3107, prtvthr == 8 ~ 3199, prtvthr == 9 ~ 3109, prtvthr == 10 ~ 3199, prtvthr == 11 ~ 3199,
                          prtvthu == 1 ~ 2306, prtvthu == 2 ~ 2303, prtvthu == 3 ~ 2399, prtvthu == 4 ~ 2305, prtvthu == 5 ~ 2301, prtvthu == 6 ~ 2399, prtvthu == 7 ~ 2304,
                          prtvtahu == 1 ~ 2302, prtvtahu == 2 ~ 2303, prtvtahu == 3 ~ 2308, prtvtahu == 4 ~ 2301, prtvtahu == 5 ~ 2399, prtvtahu == 6 ~ 2304, prtvtahu == 7 ~ 2306, prtvtahu == 8 ~ 2399,
                          prtvtbhu == 1 ~ 2302, prtvtbhu == 2 ~ 2303, prtvtbhu == 3 ~ 2308, prtvtbhu == 4 ~ 2301, prtvtbhu == 5 ~ 2399, prtvtbhu == 6 ~ 2304, prtvtbhu == 7 ~ 2306, prtvtbhu == 8 ~ 2307, prtvtbhu == 9 ~ 2399, prtvtbhu == 10 ~ 2399, prtvtbhu == 16 ~ 2399,
                          prtvtchu == 1 ~ 2302, prtvtchu == 2 ~ 2303, prtvtchu == 3 ~ 2305, prtvtchu == 4 ~ 2301, prtvtchu == 5 ~ 2399, prtvtchu == 6 ~ 2304, prtvtchu == 7 ~ 2306, prtvtchu == 8 ~ 2307, prtvtchu == 9 ~ 2399, prtvtchu == 10 ~ 2399, prtvtchu == 11 ~ 2308, prtvtchu == 12 ~ 2399, prtvtchu == 13 ~ 2309, prtvtchu == 86 ~ 2399,
                          prtvtdhu == 1 ~ 2306, prtvtdhu == 2 ~ 2399, prtvtdhu == 3 ~ 2302, prtvtdhu == 4 ~ 2308, prtvtdhu == 5 ~ 2309, prtvtdhu == 6 ~ 2303, prtvtdhu == 7 ~ 2305, prtvtdhu == 8 ~ 2301, prtvtdhu == 9 ~ 2399, prtvtdhu == 10 ~ 2399, prtvtdhu == 11 ~ 2399, prtvtdhu == 12 ~ 2399, prtvtdhu == 13 ~ 2304, prtvtdhu == 55 ~ 2399,
                          prtvtehu == 1 ~ 2302, prtvtehu == 2 ~ 2308, prtvtehu == 3 ~ 2309, prtvtehu == 4 ~ 2301, prtvtehu == 5 ~ 2399, prtvtehu == 55 ~ 2399, 
                          prtvtie == 1 ~ 701, prtvtie == 2 ~ 702, prtvtie == 3 ~ 703, prtvtie == 4 ~ 799, prtvtie == 5 ~ 705, prtvtie == 6 ~ 707, prtvtie == 7 ~ 799, prtvtie == 8 ~ 799,
                          prtvtaie == 1 ~ 701, prtvtaie == 2 ~ 702, prtvtaie == 3 ~ 705, prtvtaie == 4 ~ 799, prtvtaie == 5 ~ 703, prtvtaie == 6 ~ 709, prtvtaie == 7 ~ 707, prtvtaie == 8 ~ 708,  prtvtaie == 9 ~ 709, prtvtaie == 10 ~ 799,
                          prtvtit == 1 ~ 802, prtvtit == 2 ~ 819, prtvtit == 3 ~ 836, prtvtit == 4 ~ 808, prtvtit == 6 ~ 827, prtvtit == 7 ~ 803, prtvtit == 8 ~ 815, prtvtit == 9 ~ 805, prtvtit == 10 ~ 814, prtvtit == 11 ~ 811, prtvtit == 12 ~ 835, prtvtit == 13 ~ 828, prtvtit == 14 ~ 899, prtvtit == 15 ~ 820, prtvtit == 16 ~ 821, prtvtit == 17 ~ 899,
                          prtvtait == 1 ~ 802, prtvtait == 2 ~ 819, prtvtait == 3 ~ 836, prtvtait == 4 ~ 808, prtvtait == 6 ~ 827, prtvtait == 7 ~ 803, prtvtait == 8 ~ 815, prtvtait == 9 ~ 805, prtvtait == 10 ~ 814, prtvtait == 11 ~ 811, prtvtait == 12 ~ 835, prtvtait == 13 ~ 828, prtvtait == 14 ~ 899, prtvtait == 15 ~ 820, prtvtait == 16 ~ 821, prtvtait == 17 ~ 899,
                          prtvtbit == 1 ~ 837, prtvtbit == 2 ~ 838, prtvtbit == 3 ~ 899, prtvtbit == 4 ~ 845, prtvtbit == 5 ~ 846, prtvtbit == 6 ~ 814, prtvtbit == 7 ~ 899, prtvtbit == 8 ~ 899, prtvtbit == 9 ~ 811, prtvtbit == 10 ~ 844, prtvtbit == 11 ~ 813, prtvtbit == 12 ~ 899, prtvtbit == 13 ~ 899, prtvtbit == 14 ~ 899,
                          prtvlt1 == 1 ~ 2501, prtvlt1 == 2 ~ 2503, prtvlt1 == 3 ~ 2519, prtvlt1 == 4 ~ 2599, prtvlt1 == 5 ~ 2506, prtvlt1 == 6 ~ 2504, prtvlt1 == 7 ~ 2599, prtvlt1 == 8 ~ 2511, prtvlt1 == 9 ~ 2517, prtvlt1 == 10 ~ 2516, prtvlt1 == 11 ~ 2518, prtvlt1 == 12 ~ 2507, prtvlt1 == 13 ~ 2515, prtvlt1 == 14 ~ 2505, prtvlt1 == 15 ~ 2513, prtvlt1 == 16 ~ 2599,
                          prtvalt1 == 1 ~ 2518, prtvalt1 == 2 ~ 2599, prtvalt1 == 3 ~ 2516, prtvalt1 == 4 ~ 2599, prtvalt1 == 5 ~ 2506, prtvalt1 == 6 ~ 2520, prtvalt1 == 7 ~ 2511, prtvalt1 == 8 ~ 2501, prtvalt1 == 9 ~ 2515, prtvalt1 == 10 ~ 2599, prtvalt1 == 11 ~ 2599, prtvalt1 == 12 ~ 2599, prtvalt1 == 13 ~ 2599, prtvalt1 == 14 ~ 2507, prtvalt1 == 15 ~ 2513, prtvalt1 == 16 ~ 2505, prtvalt1 == 17 ~ 2599, prtvalt1 == 18 ~ 2599,
                          prtvlt2 == 1 ~ 2501, prtvlt2 == 2 ~ 2503, prtvlt2 == 3 ~ 2519, prtvlt2 == 4 ~ 2599, prtvlt2 == 5 ~ 2506, prtvlt2 == 6 ~ 2504, prtvlt2 == 7 ~ 2599, prtvlt2 == 8 ~ 2511, prtvlt2 == 9 ~ 2517, prtvlt2 == 10 ~ 2516, prtvlt2 == 11 ~ 2599, prtvlt2 == 12 ~ 2518, prtvlt1 == 13 ~ 2507, prtvlt2 == 14 ~ 2515, prtvlt2 == 15 ~ 2505, prtvlt2 == 16 ~ 2513, prtvlt2 == 17 ~ 2599, prtvlt2 == 18 ~ 2512, prtvlt2 == 19 ~ 2599, prtvlt2 == 20 ~ 2599,
                          prtvalt2 == 1 ~ 2518, prtvalt2 == 2 ~ 2599, prtvalt2 == 3 ~ 2516, prtvalt2 == 4 ~ 2599, prtvalt2 == 5 ~ 2506, prtvalt2 == 6 ~ 2520, prtvalt2 == 7 ~ 2511, prtvalt2 == 8 ~ 2501, prtvalt2 == 9 ~ 2515, prtvalt2 == 10 ~ 2599, prtvalt2 == 11 ~ 2599, prtvalt2 == 12 ~ 2599, prtvalt2 == 13 ~ 2599, prtvalt2 == 14 ~ 2599, prtvalt2 == 15 ~ 2599, prtvalt2 == 16 ~ 2599, prtvalt2 == 17 ~ 2507, prtvalt2 == 18 ~ 2513, prtvalt2 == 19 ~ 2505, prtvalt2 == 20 ~ 2599, prtvalt2 == 21 ~ 2599, prtvalt2 == 22 ~ 2599, prtvalt2 == 23 ~ 2599, prtvalt2 == 24 ~ 2599, prtvalt2 == 25 ~ 2599, prtvalt2 == 26 ~ 2599, prtvalt2 == 27 ~ 2599, prtvalt2 == 28 ~ 2599,
                          prtvlt3 == 1 ~ 2501, prtvlt3 == 2 ~ 2503, prtvlt3 == 3 ~ 2519, prtvlt3 == 4 ~ 2599, prtvlt3 == 5 ~ 2506, prtvlt3 == 6 ~ 2504, prtvlt3 == 7 ~ 2599, prtvlt3 == 8 ~ 2511, prtvlt3 == 9 ~ 2517, prtvlt3 == 10 ~ 2516, prtvlt3 == 11 ~ 2599, prtvlt3 == 12 ~ 2518, prtvlt3 == 13 ~ 2507, prtvlt3 == 14 ~ 2515, prtvlt3 == 15 ~ 2505, prtvlt3 == 16 ~ 2513, prtvlt3 == 17 ~ 2599, prtvlt3 == 18 ~ 2512, prtvlt3 == 19 ~ 2599, prtvlt3 == 20 ~ 2599,
                          prtvalt3 == 1 ~ 2518, prtvalt3 == 2 ~ 2599, prtvalt3 == 3 ~ 2516, prtvalt3 == 4 ~ 2599, prtvalt3 == 5 ~ 2506, prtvalt3 == 6 ~ 2520, prtvalt3 == 7 ~ 2511, prtvalt3 == 8 ~ 2501, prtvalt3 == 9 ~ 2515, prtvalt3 == 10 ~ 2599, prtvalt3 == 11 ~ 2599, prtvalt3 == 12 ~ 2599, prtvalt3 == 13 ~ 2599, prtvalt3 == 14 ~ 2599, prtvalt3 == 15 ~ 2599, prtvalt3 == 16 ~ 2599, prtvalt3 == 17 ~ 2507, prtvalt3 == 18 ~ 2513, prtvalt3 == 19 ~ 2505, prtvalt3 == 20 ~ 2599, prtvalt3 == 21 ~ 2599, prtvalt3 == 22 ~ 2599, prtvalt3 == 23 ~ 2599, prtvalt3 == 24 ~ 2599, prtvalt3 == 25 ~ 2599, prtvalt3 == 26 ~ 2599, prtvalt3 == 27 ~ 2599, prtvalt3 == 28 ~ 2599,
                          prtvtlu == 1 ~ 3801, prtvtlu == 2 ~ 3804, prtvtlu == 3 ~ 3803, prtvtlu == 4 ~ 3802, prtvtlu == 5 ~ 3806, prtvtlu == 6 ~ 3899, prtvtlu == 7 ~ 3899,
                          prtvtnl == 1 ~ 1001, prtvtnl == 2 ~ 1002, prtvtnl == 3 ~ 1003, prtvtnl == 4 ~ 1015, prtvtnl == 5 ~ 1004, prtvtnl == 6 ~ 1005, prtvtnl == 7 ~ 1014, prtvtnl == 8 ~ 1016, prtvtnl == 9 ~ 1098, prtvtnl == 10 ~ 1006, prtvtnl == 11 ~ 1099,
                          prtvtanl == 1 ~ 1001, prtvtanl == 2 ~ 1002, prtvtanl == 3 ~ 1003, prtvtanl == 4 ~ 1015, prtvtanl == 5 ~ 1004, prtvtanl == 6 ~ 1005, prtvtanl == 7 ~ 1014, prtvtanl == 8 ~ 1016, prtvtanl == 9 ~ 1098, prtvtanl == 10 ~ 1006, prtvtanl == 11 ~ 1018, prtvtanl == 12 ~ 1099,
                          prtvtbnl == 1 ~ 1001, prtvtbnl == 2 ~ 1002, prtvtbnl == 3 ~ 1003, prtvtbnl == 4 ~ 1015, prtvtbnl == 5 ~ 1004, prtvtbnl == 6 ~ 1005, prtvtbnl == 7 ~ 1014, prtvtbnl == 8 ~ 1016, prtvtbnl == 9 ~ 1098, prtvtbnl == 10 ~ 1006, prtvtbnl == 11 ~ 1099,
                          prtvtcnl == 1 ~ 1001, prtvtcnl == 2 ~ 1002, prtvtcnl == 3 ~ 1003, prtvtcnl == 4 ~ 1015, prtvtcnl == 5 ~ 1004, prtvtcnl == 6 ~ 1005, prtvtcnl == 7 ~ 1014, prtvtcnl == 8 ~ 1016, prtvtcnl == 9 ~ 1098, prtvtcnl == 10 ~ 1006, prtvtcnl == 11 ~ 1017, prtvtcnl == 12 ~ 1018, prtvtcnl == 13 ~ 1099,
                          prtvtdnl == 1 ~ 1003, prtvtdnl == 2 ~ 1002, prtvtdnl == 3 ~ 1017, prtvtdnl == 4 ~ 1001, prtvtdnl == 5 ~ 1014, prtvtdnl == 6 ~ 1004, prtvtdnl == 7 ~ 1005, prtvtdnl == 8 ~ 1016, prtvtdnl == 9 ~ 1006, prtvtdnl == 10 ~ 1018, prtvtdnl == 11 ~ 1099, prtvtdnl == 12 ~ 1099,
                          prtvtenl == 1 ~ 1003, prtvtenl == 2 ~ 1002, prtvtenl == 3 ~ 1017, prtvtenl == 4 ~ 1001, prtvtenl == 5 ~ 1014, prtvtenl == 6 ~ 1004, prtvtenl == 7 ~ 1005, prtvtenl == 8 ~ 1016, prtvtenl == 9 ~ 1006, prtvtenl == 10 ~ 1018, prtvtenl == 11 ~ 1099, prtvtenl == 12 ~ 1020, prtvtenl == 13 ~ 1099,
                          prtvtfnl == 1 ~ 1003, prtvtfnl == 2 ~ 1002, prtvtfnl == 3 ~ 1017, prtvtfnl == 4 ~ 1014, prtvtfnl == 5 ~ 1001, prtvtfnl == 6 ~ 1004, prtvtfnl == 7 ~ 1016, prtvtfnl == 8 ~ 1005, prtvtfnl == 9 ~ 1006, prtvtfnl == 10 ~ 1018, prtvtfnl == 11 ~ 1020, prtvtfnl == 16 ~ 1099,
                          prtvtno == 1 ~ 3599, prtvtno == 2 ~ 3504, prtvtno == 3 ~ 3501, prtvtno == 4 ~ 3507, prtvtno == 5 ~ 3506, prtvtno == 6 ~ 3505, prtvtno == 7 ~ 3503, prtvtno == 8 ~ 3502, prtvtno == 9 ~ 3599, prtvtno == 10 ~ 3599,
                          prtvtano == 1 ~ 3599, prtvtano == 2 ~ 3504, prtvtano == 3 ~ 3501, prtvtano == 4 ~ 3507, prtvtano == 5 ~ 3506, prtvtano == 6 ~ 3505, prtvtano == 7 ~ 3503, prtvtano == 8 ~ 3502, prtvtano == 9 ~ 3599, prtvtano == 10 ~ 3599,
                          prtvtbno == 1 ~ 3599, prtvtbno == 2 ~ 3504, prtvtbno == 3 ~ 3501, prtvtbno == 4 ~ 3507, prtvtbno == 5 ~ 3506, prtvtbno == 6 ~ 3505, prtvtbno == 7 ~ 3503, prtvtbno == 8 ~ 3502, prtvtbno == 9 ~ 3599, prtvtbno == 10 ~ 3508, prtvtbno == 11 ~ 3599,
                          prtvtpl == 1 ~ 2601, prtvtpl == 2 ~ 2608, prtvtpl == 3 ~ 2609, prtvtpl == 4 ~ 2504, prtvtpl == 5 ~ 2605, prtvtpl == 6 ~ 2606, prtvtpl == 7 ~ 2603, prtvtpl == 8 ~ 2699, prtvtpl == 9 ~ 2699, prtvtpl == 10 ~ 2607, prtvtpl == 11 ~ 2699, prtvtpl == 12 ~ 2699, prtvtpl == 13 ~ 2699, prtvtpl == 14 ~ 2699,
                          prtvtapl == 1 ~ 2699, prtvtapl == 2 ~ 2699, prtvtapl == 3 ~ 2607, prtvtapl == 4 ~ 2599, prtvtapl == 5 ~ 2699, prtvtapl == 6 ~ 2612, prtvtapl == 7 ~ 2699, prtvtapl == 8 ~ 2699, prtvtapl == 9 ~ 2603, prtvtapl == 10 ~ 2699, prtvtapl == 11 ~ 2699, prtvtapl == 12 ~ 2699, prtvtapl == 13 ~ 2606, prtvtapl == 14 ~ 2605, prtvtapl == 15 ~ 2699, prtvtapl == 16 ~ 2699, prtvtapl == 17 ~ 2611, prtvtapl == 18 ~ 2601, prtvtapl == 19 ~ 2699,
                          prtvtbpl == 1 ~ 2601, prtvtbpl == 2 ~ 2607, prtvtbpl == 3 ~ 2603, prtvtbpl == 4 ~ 2502, prtvtbpl == 5 ~ 2606, prtvtbpl == 6 ~ 2605, prtvtbpl == 7 ~ 2699, prtvtbpl == 8 ~ 2699, 
                          prtvtcpl == 1 ~ 2614, prtvtcpl == 2 ~ 2603, prtvtcpl == 3 ~ 2615, prtvtcpl == 4 ~ 2599, prtvtcpl == 5 ~ 2606, prtvtcpl == 6 ~ 2605, prtvtcpl == 7 ~ 2613, prtvtcpl == 8 ~ 2601, prtvtcpl == 9 ~ 2699,
                          prtvtpt == 1 ~ 1208, prtvtpt == 2 ~ 1202, prtvtpt == 3 ~ 1209, prtvtpt == 4 ~ 1299, prtvtpt == 5 ~ 1299, prtvtpt == 6 ~ 1299, prtvtpt == 7 ~ 1299, prtvtpt == 8 ~ 1299, prtvtpt == 9 ~ 1299, prtvtpt == 10 ~ 1205, prtvtpt == 11 ~ 1206, prtvtpt == 12 ~ 2699,
                          prtvtapt == 1 ~ 1208, prtvtapt == 2 ~ 1202, prtvtapt == 3 ~ 1299, prtvtapt == 4 ~ 1299, prtvtapt == 5 ~ 1299, prtvtapt == 6 ~ 1299, prtvtapt == 7 ~ 1299, prtvtapt == 8 ~ 1299, prtvtapt == 9 ~ 1299, prtvtapt == 10 ~ 1206, prtvtapt == 11 ~ 1205, prtvtapt == 13 ~ 2699,
                          prtvtbpt == 1 ~ 1208, prtvtbpt == 2 ~ 1202, prtvtbpt == 3 ~ 1201, prtvtbpt == 4 ~ 1299, prtvtbpt == 5 ~ 1299, prtvtbpt == 6 ~ 1299, prtvtbpt == 7 ~ 1299, prtvtbpt == 8 ~ 1299, prtvtbpt == 9 ~ 1299, prtvtbpt == 10 ~ 1206, prtvtbpt == 11 ~ 1205, prtvtbpt == 13 ~ 2699,
                          prtvtse == 1 ~ 1603, prtvtse == 2 ~ 1604, prtvtse == 3 ~ 1606, prtvtse == 4 ~ 1607, prtvtse == 5 ~ 1605, prtvtse == 6 ~ 1602, prtvtse == 7 ~ 1601, prtvtse == 8 ~ 1699,
                          prtvtase == 1 ~ 1603, prtvtase == 2 ~ 1604, prtvtase == 3 ~ 1606, prtvtase == 4 ~ 1607, prtvtase == 5 ~ 1605, prtvtase == 6 ~ 1602, prtvtase == 7 ~ 1601, prtvtase == 8 ~ 1612, prtvtase == 9 ~ 1609, prtvtase == 10 ~ 1610, prtvtase == 11 ~ 1699,
                          prtvtbse == 1 ~ 1603, prtvtbse == 2 ~ 1604, prtvtbse == 3 ~ 1606, prtvtbse == 4 ~ 1607, prtvtbse == 5 ~ 1605, prtvtbse == 6 ~ 1602, prtvtbse == 7 ~ 1601, prtvtbse == 8 ~ 1612, prtvtbse == 9 ~ 1611, prtvtbse == 10 ~ 1610, prtvtbse == 11 ~ 1699,
                          prtvtsi == 1 ~ 2906, prtvtsi == 2 ~ 2901, prtvtsi == 3 ~ 2904, prtvtsi == 4 ~ 2907, prtvtsi == 5 ~ 2902, prtvtsi == 6 ~ 2905, prtvtsi == 7 ~ 2903, prtvtsi == 8 ~ 2908, prtvtsi == 9 ~ 2999,
                          prtvtasi == 1 ~ 2902, prtvtasi == 2 ~ 2901, prtvtasi == 3 ~ 2903, prtvtasi == 4 ~ 2905, prtvtasi == 5 ~ 2904, prtvtasi == 6 ~ 2907, prtvtasi == 7 ~ 2906, prtvtasi == 8 ~ 2999,
                          prtvtbsi == 1 ~ 2906, prtvtbsi == 2 ~ 2901, prtvtbsi == 3 ~ 2904, prtvtbsi == 4 ~ 2907, prtvtbsi == 5 ~ 2902, prtvtbsi == 6 ~ 2905, prtvtbsi == 7 ~ 2903, prtvtbsi == 8 ~ 2999,
                          prtvtcsi == 1 ~ 2906, prtvtcsi == 2 ~ 2901, prtvtcsi == 3 ~ 2999, prtvtcsi == 4 ~ 2905, prtvtcsi == 5 ~ 2902, prtvtcsi == 6 ~ 2904, prtvtcsi == 7 ~ 2907, prtvtcsi == 8 ~ 2903, prtvtcsi == 9 ~ 2910, prtvtcsi == 10 ~ 2999,
                          prtvtdsi == 1 ~ 2906, prtvtdsi == 2 ~ 2901, prtvtdsi == 3 ~ 2905, prtvtdsi == 4 ~ 2902, prtvtdsi == 5 ~ 2904, prtvtdsi == 6 ~ 2903, prtvtdsi == 7 ~ 2914, prtvtdsi == 8 ~ 2999, prtvtdsi == 9 ~ 2910, prtvtdsi == 10 ~ 2907, prtvtdsi == 11 ~ 2999, prtvtdsi == 12 ~ 2999,
                          prtvtesi == 1 ~ 2906, prtvtesi == 2 ~ 2999, prtvtesi == 3 ~ 2905, prtvtesi == 4 ~ 2914, prtvtesi == 5 ~ 2903, prtvtesi == 6 ~ 2902, prtvtesi == 7 ~ 2904, prtvtesi == 8 ~ 2911, prtvtesi == 9 ~ 2999, prtvtesi == 10 ~ 2913, prtvtesi == 11 ~ 2912, prtvtesi == 12 ~ 2999,
                          prtvtsk == 1 ~ 2801, prtvtsk == 2 ~ 2802, prtvtsk == 3 ~ 2803, prtvtsk == 4 ~ 2804, prtvtsk == 5 ~ 2805, prtvtsk == 6 ~ 2806, prtvtsk == 7 ~ 2807, prtvtsk == 8 ~ 2899,
                          prtvtask == 1 ~ 2801, prtvtask == 2 ~ 2802, prtvtask == 3 ~ 2803, prtvtask == 4 ~ 2804, prtvtask == 5 ~ 2805, prtvtask == 6 ~ 2809, prtvtask == 7 ~ 2899, 
                          prtvtbsk == 1 ~ 2809, prtvtbsk == 2 ~ 2802, prtvtbsk == 3 ~ 2803, prtvtbsk == 4 ~ 2813, prtvtbsk == 5 ~ 2805, prtvtbsk == 6 ~ 2812, prtvtbsk == 7 ~ 2899, 
                          prtvtcsk == 1 ~ 2814, prtvtcsk == 2 ~ 2802, prtvtcsk == 3 ~ 2803, prtvtcsk == 4 ~ 2813, prtvtcsk == 5 ~ 2805, prtvtcsk == 6 ~ 2812, prtvtcsk == 7 ~ 2899, 
                          prtvttr == 1 ~ 3401, prtvttr == 2 ~ 3499, prtvttr == 3 ~ 3499, prtvttr == 4 ~ 3402, prtvttr == 5 ~ 3499, prtvttr == 6 ~ 3499, prtvttr == 7 ~ 3499, prtvttr == 8 ~ 3499, prtvttr == 9 ~ 3403, prtvttr == 10 ~ 3499, prtvttr == 11 ~ 3499, prtvttr == 12 ~ 3499, prtvttr == 13 ~ 3499,
                          prtvtatr == 1 ~ 3401, prtvtatr == 2 ~ 3499, prtvtatr == 3 ~ 3499, prtvtatr == 4 ~ 3402, prtvtatr == 5 ~ 3499, prtvtatr == 6 ~ 3499, prtvtatr == 7 ~ 3499, prtvtatr == 8 ~ 3499, prtvtatr == 9 ~ 3499, prtvtatr == 10 ~ 3403, prtvtatr == 11 ~ 3499, prtvtatr == 12 ~ 3499, prtvtatr == 13 ~ 3499, prtvtatr == 14 ~ 3499, prtvtatr == 15 ~ 3499,
                          prtvttr == 1 ~ 3401, prtvttr == 2 ~ 3499, prtvttr == 3 ~ 3499, prtvttr == 4 ~ 3402, prtvttr == 5 ~ 3499, prtvttr == 6 ~ 3499))

```

```{r ESS cross ref, include=FALSE, cache = TRUE}
ess.select <- ess %>% 
  left_join(ches.extended, by = "ches") %>%
  mutate(comb.weight = pspwght * pweight) %>%
  select(source, 
         ess.round = essround,
         case = cseqno, 
         post.weight = pspwght,
         pop.weight = pweight,
         comb.weight,
         
         age = agea,
         birth.year = yrbrn,
         gender = gndr, 
         
         country = cntry,
         ches,
         cmp,
         parlgov,
         party.short,
         party.cmp,
         party_name_english, 
         party_name, 
         
         eco.mean, 
         pop.mean,
         pop.vote,
         
         imsmetn, 
         imdfetn,
         impcntr,
         imbgeco,
         imueclt,
         imwbcnt,
         imbleco,
         imwbcrm,
         qfimlng, 
         qfimcmt,
         pplstrd,
         
         trstplc,
         trstplt,
         trstprt, 
         
         trstep, 
         trstun, 
         
         lrscale, 
         
         stfeco, 
         stfgov, 
         stfdem, 
         
          
          
         
         
         hrshsnt, 
         hrshsnta, 
         
         impsafe, 
         ipfrule,
         ipbhprp, 
         ipstrgv,
         imptrad,
         
         imprich,
         
         impenv, 
         freehms, 
         
         mnrgtjb, 
         wmcpwrk, 
         
         rlgblg, 
         rlgdgr, 
         rlgatnd, 
         pray, 
         
         
         polintr,
         vote = vote.x,
         
         
         contplt,
         wrkprty, 
         wrkorg, 
         badge, 
         sgnptit, 
         pbldmn, 
         bctprd, 
         mmbprty) %>%
  mutate(country = case_when(country == "BE" ~ "Belgium", 
                             country == "DK" ~ "Denmark",
                             country == "DE" ~ "Germany",
                             country == "GR" ~ "Greece",
                             country == "ES" ~ "Spain", 
                             country == "FR" ~ "France",
                             country == "IE" ~ "Ireland",
                             country == "IL" ~ "Israel",
                             country == "IT" ~ "Italy",
                             country == "IS" ~ "Iceland",
                             country == "NL" ~ "Netherlands", 
                             country == "GB" ~ "UK",
                             country == "PT" ~ "Portugal",
                             country == "AT" ~ "Austria",
                             country == "FI" ~ "Finland", 
                             country == "SE" ~ "Sweden",
                             country == "RU" ~ "Russia",
                             country == "UA" ~ "Ukraine",
                             country == "BG" ~ "Bulgaria",
                             country == "CZ" ~ "Czech Republic",
                             country == "EE" ~ "Estonia",
                             country == "HU" ~ "Hungary",
                             country == "LV" ~ "Latvia",
                             country == "LT" ~ "Lithuania",
                             country == "PL" ~ "Poland",
                             country == "RO" ~ "Romania",
                             country == "SK" ~ "Slovakia",
                             country == "SI" ~ "Slovenia",
                             country == "HR" ~ "Croatia",
                             country == "TR" ~ "Turkey",
                             country == "NO" ~ "Norway",
                             country == "CH" ~ "Switzerland",
                             country == "MT" ~ "Malta",
                             country == "LU" ~ "Luxembourg",
                             country == "CY" ~ "Cyprus")) %>%
  mutate_at(vars(pop.vote:mmbprty),funs(as.integer)) %>%
  mutate(impcntr = if_else(impcntr > 11, NA_integer_, impcntr))
rm("ess")
#gc()
```

```{r ess-vote, fig.width=10, out.width= "100%", fig.asp =.7, cache = TRUE}
ess.group.age <- ess.select %>%
  filter(!is.na(pop.vote)) %>%
  mutate(weighted.vote = pop.vote * comb.weight) %>%
  mutate(study.year = age + birth.year) %>%
  mutate(age = replace(age, age > 85, 85),
         age = replace(age, age < 21, 21)) %>%
  mutate(birth.year = study.year - age) %>%
  group_by(ess.round, age) %>%
  summarise(count = n(), 
            weights = sum(comb.weight),
            pop.vote = mean(pop.vote), 
            weighted.vote = sum(weighted.vote)/weights)

plot.a <- ggplot(data = ess.group.age, mapping = aes(x = age, y = weighted.vote, weight = weights, colour = factor(ess.round), fill = factor(ess.round))) + 
  stat_smooth(se = FALSE, span = .6) + 
#  geom_point(mapping = aes(size = weights), alpha = .2) +
  guides(size=FALSE, fill = FALSE, colour = guide_legend(title = "ESS Round - Year")) +
  labs(x = "Age", y = "Populist party vote share", title = "Age of populist voters in Europe") + 
  scale_y_percent() +
  coord_cartesian(ylim = c(0, .15)) +
  theme_ipsum() + scale_color_ipsum(labels = c("1 - 2002", "2 - 2004", "3 - 2006", "4 - 2008", "5 - 2010", "6 - 2012", "7 - 2014")) + 
  theme(legend.position = "bottom")  

ess.group.year <- ess.select %>%
  filter(!is.na(pop.vote)) %>%
  filter(!(vote == 3), age > 18) %>%
  mutate(weighted.vote = pop.vote * comb.weight) %>%
  mutate(study.year = age + birth.year) %>%
  mutate(age = replace(age, age > 85, 85),
         age = replace(age, age < 21, 21)) %>%
  mutate(birth.year = study.year - age) %>%
  group_by(ess.round, birth.year) %>%
  summarise(count = n(), 
            weights = sum(comb.weight),
            pop.vote = mean(pop.vote), 
            weighted.vote = sum(weighted.vote)/weights)

plot.b <- ggplot(data = ess.group.year, mapping = aes(x = birth.year, y = weighted.vote, weight = weights, colour = factor(ess.round), fill = factor(ess.round))) + 
  stat_smooth(se = FALSE, span = .6) + 
#  geom_point(mapping = aes(size = weights), alpha = .2) +
  guides(size=FALSE, fill = FALSE, colour = guide_legend(title = "ESS Round - Year")) +
  labs(x = "Year of Birth", y = "Populist party vote share", title = "Birth year of populist voters in Europe") +
  scale_x_reverse() + 
  scale_y_percent() +
  coord_cartesian(ylim = c(0, .15)) +
  theme_ipsum() + scale_color_ipsum(labels = c("1 - 2002", "2 - 2004", "3 - 2006", "4 - 2008", "5 - 2010", "6 - 2012", "7 - 2014")) + 
  theme(legend.position = "bottom") 

cowplot::plot_grid(plot.a, plot.b)
```

In all bar the first two ESS waves the youngest voters are the most likely to vote for populist parties. In all bar the first wave, there is also a drop off of varying intensity in the number of people voting for populist parties starting at around age 70.  The graphs clearly demonstrate period effects, especially the notable rise of populist voting in the 21st century. The first ESS wave, conducted in 2001-2002, shows less than 5% of respondents at any age voted for a populist party. By contrast, in the most recent survey, wave 7, almost 15% of the youngest respondents voted for a populist party. Finally, the graphs also show generational effects. At the extreme ends of the age spectrum, it would seem that age is a better predictor of voting patterns, with the youngest and oldest portions of the voting curves lining up better in the age plot than in the year of birth plot. However, the year of birth plot reveals a small bump in the level of populist voting in four of the seven waves for those born in the 1950s, an effect that cannot be observed in the age plot. 

Given the counter-intuitive result, it is worth taking a more granular look at the data. Perhaps this finding is driven by one particular country with an overwhelming youth vote for a populist party, an outlier that skews the overall finding. To check for outliers,I plot the populist vote by each of the countries that had a populist party, with all ESS waves combined into one curve in order to maximise sample size. Note that the top row shows countries with a higher populist vote, and thus has a different scale on the y-axis to the other two rows (Norway is plotted on both scales to illustrate the scale difference). 

```{r ess-country, fig.width=14, out.width="100%", cache = TRUE}
ess.country <- ess.select %>%
  filter(!is.na(pop.vote)) %>%
  mutate(weighted.vote = pop.vote * post.weight) %>%
  mutate(study.year = age + birth.year) %>%
  mutate(age = replace(age, age > 85, 85),
         age = replace(age, age < 20, 20)) %>%
  mutate(birth.year = study.year - age) %>%
  group_by(country, age) %>%
  summarise(count = n(), 
            weights = sum(post.weight),
            pop.vote = mean(pop.vote), 
            weighted.vote = sum(weighted.vote)/weights)

by.pop <- ess.country %>% group_by(country) %>% mutate(av.pop = mean(weighted.vote)) %>% arrange(desc(av.pop)) %>% distinct(country, .keep_all = TRUE) %>% pull(country)

high.pop <- by.pop[c(1:8)]
low.pop <- by.pop[c(8:22)]
some.pop <- by.pop[c(1:22)]

p1 <- ggplot(ess.country %>% filter(country %in% high.pop), aes(x = age, y = weighted.vote, weight = weights)) + 
  geom_smooth(se = TRUE, span = .75) + facet_wrap(~country, ncol = 8) + labs(x = NULL, y = "Populist party vote share") + theme_ipsum() + scale_y_percent() + 
  theme(panel.spacing.x=unit(0.2, "lines"),panel.spacing.y=unit(1, "lines"))
p2 <- ggplot(ess.country %>% filter(country %in% low.pop), aes(x = age, y = weighted.vote, weight = weights)) + 
  geom_smooth(se = TRUE, span = .75) + facet_wrap(~country, ncol = 8) + coord_cartesian(ylim = c(-.025,.235)) + labs(x = "Age", y = "Populist party vote share", caption = "Norway is plotted twice to illustrate the change of scale") + scale_y_percent() + theme_ipsum() + theme(axis.title.x=element_text(hjust=.5), panel.spacing.x=unit(0.2, "lines"),panel.spacing.y=unit(1, "lines"))
cowplot::plot_grid(p1, p2, nrow = 2, rel_heights = c(1, 2))
```

While there are significant differences in trends between the countries, it is also clear that young people voting for populist parties is not isolated to one country. France, Norway, Belgium, Netherlands, Bulgaria, Finland, Germany and Turkey all show a clear trend that younger people are more likely to vote for populist parties. Clearly, the data is not uniform, and there are countries that buck the overall trend. As such, we can conclude that the data is somewhat country specific. Nevertheless, as there is nothing particularly obvious connecting the countries to do share the trend, and because respondents have been weighted to take into account country population, we can conclude that the overall data is valid; this result is not driven by a sole outlying country that has a huge young populist vote. The trend shows up in multiple unrelated countries as well as the overall plot. As such, young voters across Europe *are* more likely to vote for populist parties than older voters. 


#Appendix

```{r ches-table, cache=TRUE}
ches.tbl <- ches.extended %>%
  mutate(party.name = if_else(!is.na(party_name_english), party_name_english, party.cmp)) %>%
  filter(pop.vote == 1) %>%
  arrange(country) %>%
  mutate(party.name = if_else(party.short == "VMRO-BND", "Bulgarian National Movement", party.name),
         party.name = if_else(party.short == "NFSB", "National Front for the Salvation of Bulgaria", party.name),
         party.name = if_else(party.short == "HSP-AS", "Croatian Party of Rights – Dr. Ante Starcevic", party.name),
         party.name = if_else(party.short == "SP", "United Poland", party.name),
         party.name = if_else(party.short == "KNP", "Congress of the New Right", party.name)) %>%
  mutate_if(is.numeric, funs(round(., 2))) %>%
  select(Country = country, "CHES Wave" = year, "Party Abbreviation" = party.short, "Party Name in English" = party.name, "Election Year" = electionyear, "Vote Share" = vote, "Economic Scale" = eco.mean, "Populism Scale" = pop.mean)
knitr::kable(
  ches.tbl, 
  caption = "Classification of Parties", 
  booktabs = T
)
```
